---
title: "HW4"
author: "suhy 2019010448"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 5.10

### a)
$$p(\tau|y)\propto p(\tau)V_\mu^{1/2}\prod_{j=1}^J(\sigma_j^2+\tau^2)^{-1/2}\exp{(-\dfrac{(\bar y_{.j}-\hat\mu)^2}{2(\sigma_j^2+\tau^2)})}$$
if $p(\tau)\propto \tau^{-1}$, when $\tau\to 0$, $p(\tau)\to\infty$ while $p(\tau|y)/p(\tau)\to C>0$, so $\int_{0}^{\infty}p(\tau|y)d\tau\to \infty$, so the posterior density is improper.

### b)
$$p(\tau|y)\propto V_\mu^{1/2}\prod_{j=1}^J(\sigma_j^2+\tau^2)^{-1/2}\exp{(-\dfrac{(\bar y_{.j}-\hat\mu)^2}{2(\sigma_j^2+\tau^2)})}\leq 
V_\mu^{1/2}\prod_{j=1}^J(\sigma_j^2+\tau^2)^{-1/2}=(\sum_j\prod_{k\neq j}(\sigma_k^2+\tau^2))^{-1/2}\leq J^{1/2}\tau^{1-J}$$
when J>2, $p(\tau|y)\to0$ when $\tau\to \infty$,  and in a) we find that $p(\tau|y)/p(\tau)\to C>0$, so $\int_{0}^{\infty}p(\tau|y)d\tau< \infty$, the posterior is proper.

## 5.12
$$E(\theta_j|\tau,y)=E[E[\theta_j|\mu,\tau,y]|\tau,y]=E[\dfrac{y_j/\sigma_j^2+\mu/\tau^2}{1/\sigma_j^2+1/\tau^2}|\tau,y]=\dfrac{y_j/\sigma_j^2+\hat\mu/\tau^2}{1/\sigma_j^2+1/\tau^2},\hat\mu=E[\mu|\tau,y]$$
$$Var[\theta_j|\tau,y]=E[Var[\theta_j|\mu,\tau,y]|\tau,y] + Var[E[\theta_j|\mu,\tau,y]|\tau,y]=\dfrac{1}{1/\sigma_j^2+1/\tau^2}+(\dfrac{1/\tau^2}{1/\sigma_j^2+1/\tau^2})^2V_\mu,V_\mu=Var[\mu|\tau,y]$$


## 5.13

### a)
$$p(\theta,\alpha,\beta|y)=p(\alpha,\beta)\prod p(\theta_j|\alpha,\beta)p(y|\theta_j)=(\alpha+\beta)^{-5/2}\prod_{j=1}^{10}\dfrac{\Gamma(\alpha+\beta)}{\Gamma(\alpha)\Gamma(\beta)}\theta_j^{y_j+\alpha-1}(1-\theta_j)^{n_j-y_j+\beta-1}$$

### b)
$$p(\alpha,\beta)=(\alpha+\beta)^{-5/2}\prod_{j=1}^{10}\dfrac{\Gamma(\alpha+\beta)}{\Gamma(\alpha)\Gamma(\beta)}\dfrac{\Gamma(\alpha+y_j)\Gamma(\beta+n_j-y_j)}{\Gamma(\alpha+\beta+n_j)}$$
```{r}
bike=c(16,9,10,13,19,20,18,17,35,55)
total=c(58,90,48,57,103,57,86,112,273,64) + bike
#evaluate the log posterior
logp <- function(u, v) { a <- (exp(u) * exp(v))/(exp(u) + 1);
b <- exp(v)/(exp(u) + 1);
J <- length(bike);
x <- J * (lgamma(a + b) - lgamma(a) - lgamma(b)) + log(a) + log(b) -
2.5 * log(a + b);
for(i in (1:J)) {
x <- x + lgamma(a + bike[i]) + lgamma(b + total[i] - bike[i]) -
lgamma(a + b + total[i]) }
x }
x <- c(-200:-50)/100
y <- c(50:500)/100
z <- outer(x,y,logp)
zz <- exp(z - max(z))
contour(x,y,zz,levels=c(0.05,0.15,0.25,0.35,0.45,0.55,0.65,0.75,0.85,0.95))

```

### c)
```{r}
m = 1000
zz <- zz/sum(zz)
p.x <- apply(zz,1,sum)
newx <- sample(x,m,replace=T,prob=p.x)
xid <- (newx+2.01)*100 

newy <- rep(0,m)
for (i in (1:m)){
  newy[i] <- sample(y,1,prob=zz[xid[i],]/sum(zz[xid[i],]))}


newa <- (exp(newx)*exp(newy))/(exp(newx)+1)
newb <- exp(newy)/(exp(newx)+1)

J <- length(bike);
newth = matrix(0,nrow=m,ncol=J)
for (j in (1:J)) {
newth[,j] = rbeta(m,newa+bike[j],newb+total[j]-bike[j])
}
postmean <- colMeans(newth)
plot(bike/total,postmean,xlim=c(0,0.4),ylim=c(0,0.4),col='red')
abline(a=0,b=1)
```
raw proportion is close to the posterior distribution.

### d)
```{r}
theta.mean = rowMeans(newth)
(sort(theta.mean)[c(0.025*m,0.975*m)])
```

### e)
```{r}
theta.new = rbeta(m,newa,newb)
(100*sort(theta.new)[c(0.025*m,0.975*m)])
```
the interval is too wide for application.

## 6.6

### a)
$$p_{pre}(y|\theta)\propto \theta^7(1-\theta)^{13}$$
$$
p_{new}(y|\theta)=C_{12}^7\theta^7(1-\theta)^{13}\propto \theta^7(1-\theta)^{13}$$
two protocol are the have same $p(y|theta)$

### b)
```{r}
m=10000
T = rep(0,m)
for (i in 1:m){
theta = rbeta(1,8,14)
y = rbinom(1,1,theta)
while(length(which(y==0))<13){
y = c(y,rbinom(1,1,theta))
}
l = length(y)
T[i] = length(which(y[1:(l-1)]!=y[2:(l)]))
}
hist(T,,breaks=seq(-.5,max(T)+.5),cex=2)
abline(v=3,col='red')
```

